\documentclass[conference]{IEEEtran}

\pdfpagewidth=8.5in
\pdfpageheight=11in

%% our macros and included packages
\input{macros}

\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{balance}
\usepackage{float}
\usepackage{url}
\usepackage{tabularx}
\usepackage[table]{xcolor}
\usepackage{booktabs}
\usepackage{amsmath} 
\usepackage{subfigure} 
\usepackage{multirow}
\usepackage{mdframed}

% *** CITATION PACKAGES ***
\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option % requires cite.sty v4.0 or later (November 2003) \usepackage[nocompress]{cite}
\else
  \usepackage{cite}
\fi

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor or-gan-ize}

\def\denseitems{
  \itemsep1pt plus1pt minus1pt
  \parsep0pt plus0pt
  \parskip0pt\topsep0pt}

\clubpenalty = 10000
\widowpenalty = 10000
\displaywidowpenalty = 10000

\pagenumbering{gobble}
\begin{document}

\title{Test Suite Parallelization in Open-Source Projects:\\ A Study on Its Usage and Impact}

\author{\IEEEauthorblockN{Jeanderson Candido\qquad{}Luis Melo\qquad{}Marcelo d'Amorim}
\IEEEauthorblockA{Federal University of Pernambuco\\
Pernambuco, Brazil\\
\{jbc5,lhsm,damorim\}@cin.ufpe.br}}

\maketitle
\thispagestyle{plain}
\pagestyle{plain}

\begin{abstract}
Dealing with high testing costs remains an important problem in
Software Engineering.  Test suite parallelization is an important
approach to address this problem.  This paper reports our findings on
the usage and impact of test suite parallelization in open-source
projects.\Comment{ This study brings to light the benefits and burdens
  of that approach.} It provides recommendations to practitioners and
tool developers to speed up test execution.

Considering a set of \numSubjs{} popular Java projects we analyzed, we
found that \percentMedLongRunning{} of the projects contain costly
test suites but parallelization features still seem underutilized in
practice~---~only \percentParallelUpdated{} of costly projects use
parallelization.  The main reported reason for adoption resistance was
the concern to deal with concurrency issues.  Results suggest that, on
average, developers prefer high predictability than high performance
in running tests.
\end{abstract}

\IEEEpeerreviewmaketitle

\input{intro}
\input{modes}
\input{subjects}
\input{evaluation}
\input{lessons}
\input{threats}
\input{related}
\input{conclusions}

%% uncomment for camera-ready
%% % use section* for acknowledgment
\ifCLASSOPTIONcompsoc
% The Computer Society usually uses the plural form
\section*{Acknowledgments}
\else
% regular IEEE prefers the singular form
\section*{Acknowledgment}
\fi

Jean(derson) and Luis are supported by FACEPE scholarphips
IBPG-0632-1.03/15 and IBPG-1175-1.03/16, respectively.  This work was
partially supported by CNPq grants 457756/2014-4 and 203981/2014-6.
%\newpage
% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)

\balance
\bibliographystyle{plain}
\bibliography{tmp}

% that's all folks
\end{document}



%%  LocalWords:  Parallelization multi parallelization tmp tradeoffs
